Numerical investigation of viscous flow instabilities through heterogeneous porous media. Advantages and limitations of unstructured and adaptive meshes in 2D and 3D domains under different mobility scenarios.

### 2017-12-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

%As outlined in Section \ref{section:ViscousInstabilities}, viscous instabilities are characterised by spontaneous formation and growth of fluid elongations, called viscous fingers. The geometrical evolution of these elongations provides good indication of instabilities at the fluid front interface.
Figure \ref{fig:3DChannel_PermMesh} shows initial permeability distribution for the simulations described in this section. The surface on the left-hand side of the domain is the area where fluid $1$ is injected with a uniform velocity of 2.5 cm.s$^{-1}$. No-flux boundary conditions are applied to all borders, except the right-hand side (inlet) and the left-hand side (outflow). Initially, the domain was partially saturated with non-wetting fluid, \ie $S_{nw}(t=0)=0.80$, which was displaced by a pure (wetting) fluid. The domain (with 368513 \PNDG[1]{1} tetrahedral element-pairs) was designed to capture preferential flow pathways, \ie regions with larger permeability (Fig.~\ref{fig:3DChannel_PermMesh}) as demonstrated in Fig.~\ref{fig:3DChannel_planes}-\ref{fig:3DChannel_Isosurf}.

>>>>

%As outlined in Section \ref{section:ViscousInstabilities}, viscous instabilities are characterised by spontaneous formation and growth of fluid elongations, called viscous fingers. The geometrical evolution of these elongations provides good indication of instabilities at the fluid front interface.
Figure \ref{fig:3DChannel_PermMesh} shows the permeability distribution for the simulations conducted in this Section, where pure (wetting) fluid is added into the domain with uniform velocity of 2.5 cm.s$^{-1}$. No-flux boundary conditions are applied to all borders, except the right-hand (inlet) and the left-hand sides (outflow). Initially, the domain was partially saturated with non-wetting fluid $\left(S_{nw}(t=0)=0.80\right)$, which was displaced by the wetting fluid as the simulation progress. The domain (with 368513 \PNDG[1]{1} tetrahedral element-pairs) was designed to naturally capture preferential flow pathways through channels of large absolute permeability (Fig.~\ref{fig:3DChannel_PermMesh}) as shown in Fig.~\ref{fig:3DChannel_planes}-\ref{fig:3DChannel_Isosurf}.

The surface on the left-hand side of the domain is the area where fluid $1$ is injected with a uniform velocity of 2.5 cm.s$^{-1}$.
